\toolnameend: A Tool for Visualizing Patterns of Spreadsheet Function Combinations

### 2016-08-08 doc/paper.tex
Fixes #147

	The detection of bad design, however, is certainly not limited to a
	visualization tool, and some users remarked that a tool which printed a list of
	errors could work just as well for that purpose. However, they also said
	that this visual interface is better when searching for new smells. 
	Because the exploratory design makes no
	qualitative judgment and visualizes benign designs with the problematic, it
	allows for flexible interpretation of what a smell is; that is, a
	user might not realize a certain design is poor until they see it in the
	tree and, at the point, find specific examples of where it occurs in the
	spreadsheets.

>>>>

	The detection of bad design, however, is certainly not limited to a
	visualization tool. Some users remarked that a tool which printed a list of
	errors could work just as well for that purpose, and smell checkers can and
	have been directly built into spreadsheets to point out bad design.
	However, users also said that this visual interface is better when searching
	for new smells. Because the exploratory design makes no qualitative judgment
	and visualizes benign designs with the problematic, it allows for flexible
	interpretation of what a smell is; that is, a user might not realize a certain
	design is poor until they see it in the tree and, at the point, find specific
	examples of where it occurs in the spreadsheets.
